Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-29 tests-shockpool.tex
Editing the shockpool test. Mostly small fixes.

The next problem is similar to the last one, but examines how a shock wave with a Mach number of 2 passes into and out of a static refined region (again defined from $z=0.25$ to 0.75).  The density and pressure in the domain is initially set equal to 1.0, with zero velocity, and then at $t=0$, the left boundary is set with the density, pressure and velocity appropriate for $M=2$ shock wave.

@@

Beginning with PPM (top row), we see that this method captures the shock in a small number of zones with only a small amount of oscillation.  Open entering the refined region, the shock finds itself broader than the natural width of the scheme (since the cell spacing is decreased by a factor of 2), and so the shock front contracts, causing a slight entropy perturbation in the post-shock gas.

For Zeus (middle row of Figure~\ref{fig.shockpool}, the shock is broadened because of artificial viscosity, and there are slightly more post-shock oscillations, although again quite mild.  The impact of entering and exiting the refined region is somewhat larger than in PPM; however, the most noticeable difference is the incorrect position of the shock front, which is due to the fact that the scheme is not energy-conserving (see also the Sedov problem, below), and has essentially nothing to do with the passage through the refined region.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/ShockPool}
\caption{This plot shows, for each column, three snap shots (at $t=0.1, 0.15$ and 0.35) of a $M=2$ shock wave as it propagates through the grid with a static refined region extends from $x = 0.25$ to 0.75 (shown in grey in each panel).   Each row shows the result for a different solver (PPM/Zeus/MUSCL from top to bottom).  The solid line shows the analytic solution.  Note that we focus each panel on a small region of the entire domain to better show the shock front.}
\label{fig.shockpool}
\end{center}
\end{figure}

>>>>

The next problem is similar to the last one but instead examines how a shock with a Mach number of 2 passes in and out of a static refined region (again defined from $z=0.25$ to 0.75).  The density and pressure in the domain is initially set equal to 1.0 with zero velocity.  At $t=0$ the left boundary is set with the density, pressure and velocity appropriate for $\mathcal{M}=2$ shock wave.

@@

Beginning with PPM (top row of Figure \ref{fig.shockpool}), we see that this method captures the shock in a small number of zones with only a small amount of oscillation.  Upon entering the refined region, the shock finds itself broader than the natural width of the scheme (since the cell spacing is decreased by a factor of 2), and so the shock front contracts, causing a slight entropy perturbation in the post-shock gas.

For Zeus (middle row of Figure~\ref{fig.shockpool}, the shock is broadened because of artificial viscosity and there are slightly more post-shock oscillations, although again quite mild.  The impact of entering and exiting the refined region is somewhat larger than in PPM; however, the most noticeable difference is the incorrect position of the shock front. This is due to the fact that the scheme is not energy-conserving (see also the Sedov problem, below), and has very little to do with the passage through the refined region.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/ShockPool}
\caption{This plot shows, for each column, three snapshots at $t=0.1, 0.15$ and 0.35 of a $\mathcal{M}=2$ shock as it propagates through the grid with a static refined region extends from $x = 0.25$ to 0.75 (shown in grey in each panel).   Each row shows the result for a different solver (PPM/Zeus/MUSCL from top to bottom).  The solid line shows the analytic solution.  Note that we focus each panel on a small region of the entire domain to better show the shock front.}
\label{fig.shockpool}
\end{center}
\end{figure}
